Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-03-27 main.Rmd
all plot labels lowercase + for weekends/weekdays no xlabels needed

```{r tab-mayan}
table_mayan <- tibble(`linear (G)` = c("kin", "uinal", "tun", "katun", "baktun"),
                      `single-order-up cyclic (C)` = c("kin-of-uinal","uinal-of-tun"," tun-of-katun", "katun-of-baktun", 1),
                       `period length/conversion operator (K)`= c(20, 18, 20, 20, 1)) 
kable(table_mayan, 
      format = "latex",
      booktabs = TRUE,
      caption = "Hierarchy table for Mayan calendar with all circular single-order-up granularities.") %>% 
  kable_styling()
  #row_spec(0, bold = TRUE) %>% 
  #row_spec(1:(nrow(table_mayan)-1), hline_after = T)   
```

@@

scene1 <-  VIC %>%
  #create_gran("quarter_year") %>%
  #filter(month_year %in% c("Jan", "Mar", "Dec")) %>% 
  #create_gran("day_week") %>%
  #filter(day_week %in% c("Sat", "Sun", "Mon")) %>%
  prob_plot("quarter_year", "wknd_wday",
            response = "general_supply_kwh",
            plot_type = "lv",
            symmetric = FALSE
  ) +
  ylab("") +
  xlab("weekend/weekday") +
  scale_fill_brewer(palette = "Dark2") + theme(legend.position = "right") + ggtitle("") + scale_y_log10()

scene2 <- VIC %>%
  #create_gran("month_year") %>%
  #filter(month_year %in% c("Jan", "Mar", "Dec")) %>% 
  #create_gran("day_week") %>%
  #filter(day_week %in% c("Sat", "Sun", "Mon")) %>%
  prob_plot("wknd_wday",
            "quarter_year",
            response = "general_supply_kwh",
            plot_type = "lv",
            symmetric = FALSE
  ) +
  ylab("") +
    xlab("quarter-of-year")  +
  scale_fill_brewer(palette = "Paired") + theme(legend.position = "right") + ggtitle("") + scale_y_log10()

@@

scene3 <- VIC %>%
  #create_gran("month_year") %>%
  #filter(month_year %in% c("Jan", "Mar", "Dec")) %>% 
  #create_gran("day_week") %>%
  #filter(day_week %in% c("Sat", "Sun", "Mon")) %>%
  prob_plot("quarter_year",
            "month_year",
            response = "general_supply_kwh",
            plot_type = "lv",
            symmetric = FALSE
  ) +
  ylab("") +
  xlab("months") + theme(legend.position = "right") + scale_fill_brewer(palette = "Set2") + ggtitle("") + scale_y_log10()

gg_fig <- ggarrange(scene3, 
          ggarrange(scene1, scene2, ncol = 2, labels = c("(b)", "(c)")),
          nrow = 2, labels = "(a)")
          #label.y = "Electricity Demand [KWh]"\

ggpubr::annotate_figure(gg_fig,
                left = text_grob("Electricity Demand [KWh]",  rot = 90))

@@

# plot for only customer is shown
# cust1 <- smart_meter10 %>%
# filter(customer_id %in% c(10006704)) %>%
#   prob_plot("wknd_wday",
#                             "hour_day",
#                             response = "general_supply_kwh",
#                             plot_type = "quantile",
#             symmetric = FALSE,
#             quantile_prob = c(0.25, 0.5, 0.75, 0.9))
#   scale_y_sqrt() +
#   ggtitle("Energy consumption distribution for customer id: 10006704")
cust2_quantile <- smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>%
  prob_plot("wknd_wday",
    "hour_day",
    response = "general_supply_kwh",
    plot_type = "quantile",
    symmetric = TRUE,
    quantile_prob = c(0.01, 0.1, 0.25, 0.5, 0.75, 0.9, 0.99)
  ) +
  scale_y_sqrt() +
  #ggtitle(" (b) Area quantile plot faceted by weekend-weekday") +
  ylab("Electricity Demand [KWh]") + xlab("hour-of-day") + ggtitle("") + ylab("")
#
# smart_meter10 %>%
#   filter(customer_id %in% c(10006704)) %>%
#   prob_plot("wknd_wday",
#                             "hour_day",
#                             response = "general_supply_kwh",
#                             plot_type = "violin") +
#   scale_y_sqrt() +
#   ggtitle("Energy consumption distribution for customer id: 10006704")

@@

cust2_box <- smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>%
  prob_plot("hour_day",
    "wknd_wday",
    response = "general_supply_kwh",
    plot_type = "boxplot"
  ) +
  scale_y_sqrt() +
  #ggtitle(" (a) Box plot faceted by hour-of-day") +
  xlab("weekday(wdy)/ weekend(wnd)") + ggtitle("") + ylab("") + 
  scale_x_discrete(labels = c('wdy','wnd'))

@@

gg_fig <- ggarrange(cust2_box, 
          ggarrange(cust2_quantile, cust2_violin, nrow = 2, labels = c("(b)", "(c)")),
          ncol = 2, labels = "(a)")
          #label.y = "Electricity Demand [KWh]"\

ggpubr::annotate_figure(gg_fig,
                left = text_grob("Electricity Demand [KWh]",  rot = 90))
```

@@

cricket_tsibble %>%
  filter(batting_team %in% c(
    "Mumbai Indians",
    "Chennai Super Kings"
  )) %>%
  mutate(inning = paste0("inning:", inning)) %>% 
  prob_plot("inning",
    "over",
    response = "runs_per_over",
    hierarchy_model,
    plot_type = "lv"
  ) + 
  scale_fill_brewer(palette = "Dark2") + 
  ggtitle("(a) Runs per over across over faceted by inning") +
  theme(legend.position = "right") +
  ggtitle("(a)") +
  ylab("runs per hour") +
  xlab("over-of-inning") 
  # ggplot2::theme(
  #     strip.text = ggplot2::element_text(
  #       size = 7,
  #       margin = ggplot2::margin()
  #     )
  #   ) 
  #

@@

# filter(fielding_wckts %in% c(0,1)) %>%
# 
 cricket_data %>%
  filter(over!=1) %>% 
  prob_plot("over", "lag_field",
  hierarchy_model,
  response = "run_rate",
  plot_type = "boxplot",
  symmetric = FALSE,
 quantile_prob = c(0.25, 0.5, 0.75)
) + ggtitle("(b) Runs per over across overs faceted by number of wickets in previous over") + 
  ylab("runs per over")  +
  xlab("Number of wickets in previous over") +
  ggtitle("(b)")
# + geom_boxplot(width = 0.5, aes(colour = lag_field)) 
```

>>>>

```{r tab-mayan}
table_mayan <- tibble(`linear (G)` = c("kin", "uinal", "tun", "katun", "baktun"),
                      `single-order-up cyclic (C)` = c("kin-of-uinal","uinal-of-tun"," tun-of-katun", "katun-of-baktun", 1),
                       `period length/conversion operator (K)`= c(20, 18, 20, 20, 1)) 
kable(table_mayan, 
      format = "latex",
      booktabs = TRUE,
      align = "l",
      caption = "Hierarchy table for Mayan calendar with all circular single-order-up granularities.") %>% 
  kable_styling()
  #row_spec(0, bold = TRUE) %>% 
  #row_spec(1:(nrow(table_mayan)-1), hline_after = T)   
```

@@

scene1 <-  VIC %>%
  #create_gran("quarter_year") %>%
  #filter(month_year %in% c("Jan", "Mar", "Dec")) %>% 
  #create_gran("day_week") %>%
  #filter(day_week %in% c("Sat", "Sun", "Mon")) %>%
  prob_plot("quarter_year", "wknd_wday",
            response = "general_supply_kwh",
            plot_type = "lv",
            symmetric = FALSE
  ) +
  ylab("") +
  #xlab("weekend/weekday") +
  scale_fill_brewer(palette = "Dark2") + theme(legend.position = "right") + ggtitle("") + scale_y_log10() + xlab("")

scene2 <- VIC %>%
  #create_gran("month_year") %>%
  #filter(month_year %in% c("Jan", "Mar", "Dec")) %>% 
  #create_gran("day_week") %>%
  #filter(day_week %in% c("Sat", "Sun", "Mon")) %>%
  prob_plot("wknd_wday",
            "quarter_year",
            response = "general_supply_kwh",
            plot_type = "lv",
            symmetric = FALSE
  ) +
  ylab("") +
    xlab("quarters of the year")  +
  scale_fill_brewer(palette = "Paired") + theme(legend.position = "right") + ggtitle("") + scale_y_log10()

@@

scene3 <- VIC %>%
  #create_gran("month_year") %>%
  #filter(month_year %in% c("Jan", "Mar", "Dec")) %>% 
  #create_gran("day_week") %>%
  #filter(day_week %in% c("Sat", "Sun", "Mon")) %>%
  prob_plot("quarter_year",
            "month_year",
            response = "general_supply_kwh",
            plot_type = "lv",
            symmetric = FALSE
  ) +
  ylab("") +
  xlab("months of the year") + theme(legend.position = "right") + scale_fill_brewer(palette = "Set2") + ggtitle("") + scale_y_log10()

gg_fig <- ggarrange(scene3, 
          ggarrange(scene1, scene2, ncol = 2, labels = c("(b)", "(c)")),
          nrow = 2, labels = "(a)")
          #label.y = "electricity demand [KWh]"\

ggpubr::annotate_figure(gg_fig,
                left = text_grob("electricity demand [KWh]",  rot = 90))

@@

# plot for only customer is shown
# cust1 <- smart_meter10 %>%
# filter(customer_id %in% c(10006704)) %>%
#   prob_plot("wknd_wday",
#                             "hour_day",
#                             response = "general_supply_kwh",
#                             plot_type = "quantile",
#             symmetric = FALSE,
#             quantile_prob = c(0.25, 0.5, 0.75, 0.9))
#   scale_y_sqrt() +
#   ggtitle("Energy consumption distribution for customer id: 10006704")
cust2_quantile <- smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>%
  prob_plot("wknd_wday",
    "hour_day",
    response = "general_supply_kwh",
    plot_type = "quantile",
    symmetric = TRUE,
    quantile_prob = c(0.01, 0.1, 0.25, 0.5, 0.75, 0.9, 0.99)
  ) +
  scale_y_sqrt() +
  #ggtitle(" (b) Area quantile plot faceted by weekend-weekday") +
  ylab("electricity demand [KWh]") + xlab("hours of the day") + ggtitle("") + ylab("")
#
# smart_meter10 %>%
#   filter(customer_id %in% c(10006704)) %>%
#   prob_plot("wknd_wday",
#                             "hour_day",
#                             response = "general_supply_kwh",
#                             plot_type = "violin") +
#   scale_y_sqrt() +
#   ggtitle("Energy consumption distribution for customer id: 10006704")

@@

cust2_box <- smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>%
  prob_plot("hour_day",
    "wknd_wday",
    response = "general_supply_kwh",
    plot_type = "boxplot"
  ) +
  scale_y_sqrt() +
  #ggtitle(" (a) Box plot faceted by hour-of-day") +
  xlab("") +
  ggtitle("") + ylab("") + 
  scale_x_discrete(labels = c('wdy','wnd'))

@@

gg_fig <- ggarrange(cust2_box, 
          ggarrange(cust2_quantile, cust2_violin, nrow = 2, labels = c("(b)", "(c)")),
          ncol = 2, labels = "(a)")
          #label.y = "electricity demand [KWh]"\

ggpubr::annotate_figure(gg_fig,
                left = text_grob("electricity demand [KWh]",  rot = 90))
```

@@

cricket_tsibble %>%
  filter(batting_team %in% c(
    "Mumbai Indians",
    "Chennai Super Kings"
  )) %>%
  mutate(inning = paste0("inning:", inning)) %>% 
  prob_plot("inning",
    "over",
    response = "runs_per_over",
    hierarchy_model,
    plot_type = "lv"
  ) + 
  scale_fill_brewer(palette = "Dark2") + 
  ggtitle("(a) Runs per over across over faceted by inning") +
  theme(legend.position = "right") +
  ggtitle("(a)") +
  ylab("runs per over") +
  xlab("overs of the innings") 
  # ggplot2::theme(
  #     strip.text = ggplot2::element_text(
  #       size = 7,
  #       margin = ggplot2::margin()
  #     )
  #   ) 
  #

@@

# filter(fielding_wckts %in% c(0,1)) %>%
# 
 cricket_data %>%
  filter(over!=1) %>% 
  prob_plot("over", "lag_field",
  hierarchy_model,
  response = "run_rate",
  plot_type = "boxplot",
  symmetric = FALSE,
 quantile_prob = c(0.25, 0.5, 0.75)
) + ggtitle("(b) Runs per over across overs faceted by number of wickets in previous over") + 
  ylab("runs per over")  +
  xlab("number of wickets in previous over") +
  ggtitle("(b)")
# + geom_boxplot(width = 0.5, aes(colour = lag_field)) 
```
